\section*{Work Plan}

% Camera movement
% Shader hot reload
% Imgui
% Flat grid
% Octree
% Brick rendering
% Contree
% 3D texture
% Events

% Modification
% Octree / Contree
% Brick / Grid / 3D texture

% Serialization
% Octree / Contree
% Brick / Grid / 3D texture

% Lighting?
% Shadows
% AO
% Lights

% Split rendering
% Server / Client
% Networking
% Rendering between clients

\begin{tabular}{lll}
  Sprint & Dates & Plan \\
  \hline
  1 & Oct 13 -- Oct 27 & Project setup \\
  && Basic Vulkan rendering to the screen via Compute shaders. \\
  && Shader hot reloading \\
  && ImGui setup \\
  && Camera movement \\
  && Event system \\
  \hline
  2 & Oct 27 -- Nov 10 & Start implementing ray marching structures \\
  && Flat grid structure \\
  && Octree structure \\
  \hline
  3 & Nov 10 -- Nov 24 & Continue with implementing basic methods \\
  && Brickmap support \\
  && Contree support \\
  \hline
  4 & Nov 24 -- Dec 08 & Additional structures \\
  && 3D textures \\
  && Modification for flat grid \\
  \hline
  5 & Dec 08 -- Dec 22 & Modification \\
  && Modification for octree / contree \\
  && Modification for brickmap \\
  \hline
  6 & Dec 22 -- Jan 05 & Break \\
  \hline
  7 & Jan 05 -- Jan 19 & Start split rendering\\
  && Split software into client and server \\
  && Establish connection between client and server \\
  \hline
  8 & Jan 19 -- Feb 02 & Data \\
  && Implement 3D grid for split rendering \\
  \hline
  9 & Feb 02 -- Feb 16 & Implement structure across devices \\
  && Implement Octree/Contree for split rendering \\
  \hline
  10 & Feb 16 -- Mar 02 & Octree addition \\
  && Implement loading for tree nodes \\
  \hline
  11 & Mar 02 -- Mar 16 & Octree across devices \\
  && Allow for nodes to be individually loaded between devices \\
  \hline
  12 & Mar 16 -- Mar 30 & Refactor / extra time \\
  \hline
\end{tabular}

By the end of Michaelmas the core project should be finished to a
sufficient degree. This leaves Lent to work on the more complicated extensions.
In particular lent will be focused on the split rendering, with an interest in
implementing the octree/contree as this structure, along with
selective inclusion
of the tree nodes that are out of level of detail range, and those that are
obscured would require more communication between the client and server, and so
a more interesting challenge.

There are also some additional tasks, that if time allows can be included.
Notably this may include better lighting calculations, and serialization and
loading of the voxel data. These are not planned for as the time requirement for
split rendering is not easy to judge. This is why the last sprint is left open,
either for additional tasks, or for continuing work on the previous tasks.

Github projects will be used to split these tasks into further subcomponents and
to organise those tasks within the sprints. This will also allow for
bug tracking and any additional features that may be needed to be
included and planned for.
